Wavelets

### 2019-03-05 Chlorophyll_a .Rmd
updated

The aim of this script is to extract the chlorophyll a netCDF files and convert it to CSV. The chlorophylla data were obtained from MODIS Aqua. The aim of working with these chlorophyll a data is to examine how the chlorophyll a concentration varies with upwelling.

```{r}
library(ncdf4)
library(data.table)
library(tidyverse)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(lubridate)
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(ggpubr)
library(fasttime)
library(FNN)
library(heatwaveR)

MODIS_chlor.dir <- "/home/amieroh/Documents/Data/Datasets/Chlorophyll_a"
MODIS_chlor.csv.dir <- "/home/amieroh/Documents/Data/Datasets"

@@

llply(ncList, ncFun, csv.dir = MODIS_chlor.csv.dir, .parallel = TRUE)
```

@@

Chlorophyll-a data are 8 day composites. In order to compare the chlorophyll concentration with upwelling events, take 8 days, take the average. This is one value. Repeat this so what I have a time series with chlorophyll-a data every 8 days.

Plot this using a line graph?... Upwelling evetns were plot using wavelet analyses

```{r}
# MODIS_Chloro <- "~/Documents/Masters_2019/MastersProject/Data"
# MODIS_Chloro <- fread(paste0(MODIS_Chloro, "/BC-MODIS.Aqua.L3m_8D_CHL_chlor_a_9km-2002185-2018345.csv"),
#             col.names = c("lon", "lat", "chloro", "date"))

# save(MODIS_Chloro, file = "Data/MODIS_Chloro.RData")
load("Data/MODIS_Chloro.RData")
load("Data/combined_US.RData")

match_index <- knnx.index(data = as.matrix(MODIS_Chloro[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

pixel_match <- MODIS_Chloro[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)

daily_chloro_match <- MODIS_Chloro %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)

# With the chloro pixels filter, it is now faster to create the daily data
daily_chloro_data <- daily_chloro_match %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(combi, lon, lat, date) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>% 
  dplyr::group_by(combi, lon, lat) %>% 
  tidyr::nest() %>% 
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                       climatologyPeriod = c("2002-07-13", "2018-12-04"), # This doesn't mean anything, but the function needs it to work
                       maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>% 
  tidyr::unnest() %>% 
  select(-doy, -seas, -thresh)

ggplot(daily_chloro_data, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~combi, ncol = 1)

@@

>>>>

## Script info
The aim of this script is to extract the chlorophyll a netCDF files and convert it to CSV. The chlorophylla data were obtained from MODIS Aqua. The aim of working with these chlorophyll a data is to examine how the chlorophyll a concentration varies with upwelling.

```{r}
library(ncdf4)
library(data.table)
library(tidyverse)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(lubridate)
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(ggpubr)
library(fasttime)
library(FNN)
library(heatwaveR)
```

This function convert chlorophyll netCDF datasets to a single CSV datset

```{r}
MODIS_chlor.dir <- "/home/amieroh/Documents/Data/Datasets/Chlorophyll_a"
MODIS_chlor.csv.dir <- "/home/amieroh/Documents/Data/Datasets"

@@

llply(ncList, ncFun, csv.dir = MODIS_chlor.csv.dir, .parallel = TRUE)

# MODIS_Chloro <- "~/Documents/Masters_2019/MastersProject/Data"
# MODIS_Chloro <- fread(paste0(MODIS_Chloro, "/BC-MODIS.Aqua.L3m_8D_CHL_chlor_a_9km-2002185-2018345.csv"),
#             col.names = c("lon", "lat", "chloro", "date"))

# save(MODIS_Chloro, file = "Data/MODIS_Chloro.RData")
```

@@

```{r}

# Loading the data
load("Data/MODIS_Chloro.RData") # Extracted chlorophyll data
load("Data/combined_US.RData") # Site list of all the sites along the west coast

chloro_plot <- MODIS_Chloro %>%
  filter(date == min(date)) %>%
  ggplot(aes(x = lon, y = lat)) +
  geom_raster(aes(fill = chloro))

unique_pixel <- MODIS_Chloro %>% 
  select(lon, lat) %>% 
  unique()

match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

# Matching the sites within the chlorophyll data to the sites along the west coast
pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)

chloro_match <- MODIS_Chloro %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)

chloro_match %>%
  filter(date == max(date)) %>%
  ggplot(aes(x = lon, y = lat)) +
  geom_raster(aes(fill = chloro))

combined_chloro_sites <- chloro_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat")) %>% 
  dplyr::mutate(date = as.Date(date))

# Save the complete dataset
# save(combined_chloro_sites, file = "Data/combined_chloro_sites.RData")

Chloro_plot_complete <- ggplot(combined_chloro_sites, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~site, ncol = 1)
Chloro_plot_complete

# Plotting only years 2014-2015
daily_chloro_data_tester <- combined_chloro_sites %>% 
  filter(year(date) %in% seq(2014, 2015))

Chloro_ggplot(daily_chloro_data_tester, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~site, ncol = 1)
Chloro_plot_filtered

# # With the chloro pixels filter, it is now faster to create the daily data
# daily_chloro_data <- daily_chloro_match %>%
#   dplyr::mutate(date = as.Date(date)) %>%
#   dplyr::group_by(combi, lon, lat, date) %>%
#   dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
#   dplyr::group_by(combi, lon, lat) %>%
#   tidyr::nest() %>%
#   dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
#                      climatologyPeriod = c("2002-07-13", "2018-12-04"), # This doesn't mean anything, but the function needs it to work
#                      maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
#   dplyr::select(-data) %>%
#   tidyr::unnest() %>%
#   select(-doy, -seas, -thresh)

## Plotting daily data
# ggplot(daily_chloro_data, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~combi, ncol = 1)

@@

Here I match the chlorophyll a data with the temperature data. This is done to explore how chlorophyll a concentration varies with temperature.

```{r}
load("Data/combined_chloro_sites.RData")

## Load in the rest of the datasets
## See the Dectect_MCS.Rmd script for more info. The datasets loaded here are only for temperatures collected between the years 1992-2016. However if a longer time series is required changes may  be made to the Dectect_MCS.Rmd script (line 136)

load("Data/overlap_ts.RData")
load("Data/insitu_MUR.RData")
load("Data/insitu_OISST.RData")
load("Data/insitu_G1SST.RData")
load("Data/insitu_K10.RData")

filtered_years <- function(df){
  upwelling<- df %>% 
  filter(year(date) %in% seq(2014, 2015)) %>% 
  drop_na()
}

SACTN_fyears <- filtered_years(df = overlap_ts) 
MUR_fyears <- filtered_years(df = insitu_MUR) 
OISST_fyears <- filtered_years(df = insitu_OISST) 
G1SST_fyears <- filtered_years(df = insitu_G1SST) 
K10_fyears <- filtered_years(df = insitu_K10)

# save(SACTN_fyears, file = "Data/temp_2014_2015/SACTN_fyears.RData")
# save(MUR_fyears, file = "Data/temp_2014_2015/MUR_fyears.RData")
# save(OISST_fyears, file = "Data/temp_2014_2015/OISST_fyears.RData")
# save(G1SST_fyears, file = "Data/temp_2014_2015/G1SST_fyears.RData")
# save(K10_fyears, file = "Data/temp_2014_2015/K10_fyears.RData")
```

The next step is to now match the insitu temperature data with the SST data

```{r}
temp_chloro <- function(df){
  combined <- df %>% 
  left_join(combined_chloro_sites, by = c("site", "date")) %>% 
  select(-combi, -lat, -lon) %>% # Temp.x is the insitu collected data
  #dplyr::rename(temp = temp.y) %>%
  na.trim()
  return(combined)
}

temp_chloro_SACTN <- temp_chloro(df = SACTN_fyears)
temp_chloro_MUR <- temp_chloro(df = MUR_fyears)
temp_chloro_OISST <- temp_chloro(df = OISST_fyears)
temp_chloro_G1SST <- temp_chloro(df = G1SST_fyears)
temp_chloro_G1SST <- temp_chloro(df = K10_fyears)
```

### 2019-03-05 Wind_analyses.Rmd
updated

# Script Info
The aim of this script is to plot wind rose diagrams representing the wind directions for the sites along the west coast of South Africa. The data used to plot the wind rose diagrams will correspond with the data used to plot the wavelet analyses. Using this we will be able to make deductions as to weather or not the intensity and duration of upwelling varied as a result of wind direction.

The wind data used in this analyses were obtained from the SAWS as well as the NCEP wind data. *Other wind datasets still to be used*

@@

library(tidyverse)
library(ggpubr)
library(lubridate)
library(stringr)
library(circular)
library(broom)
library(purrr)
library(stlplus)
source("functions/wind.rose.R")
```

@@

Creating a function which allows me to load the wind data:

```{r define_fun8, include=TRUE}
load_wave <- function(wave_files) {
  site_name <- sapply(strsplit(as.character(wave_files), "/"), "[[", 3)
  site_info <- sapply(strsplit(as.character(wave_files), "/"), "[[", 4)
  site_info <- sapply(strsplit(site_info, ".txt"), "[[", 1)
  site_info <- strsplit(site_info, "_")
  site_depth <- sapply(site_info, "[[", 1)
  site_num <- sapply(site_info, "[[", 2)

  wave <- read_table(wave_files, col_types = c("dddddd"),
                     col_names = c("date", "hs", "tp", "dir", "dirw", "spw")) %>%
    filter(tp != -999) %>%
    mutate(date = as.POSIXct(as.character(date), "%Y%m%d%H%M", tz = "Africa/Johannesburg")) %>%
    mutate(site = site_name,
           num = site_num,
           depth = site_depth) %>%
    select(site, num, depth, everything()) %>% 
    na.omit()
  return(wave)
}
```

Loadng the wind data for some of the sites along the wc of South Africa

```{r}
sea_point <- map_dfr(dir("Data/wave_data/Sea Point", 
                            full.names = TRUE, pattern = "*.txt"), load_wave)
lamberts_bay <- map_dfr(dir("Data/wave_data/Lamberts Bay", 
                          full.names = TRUE, pattern = "*.txt"), load_wave)
port_nolloth <- map_dfr(dir("Data/wave_data/Port Nolloth", 
                            full.names = TRUE, pattern = "*.txt"), load_wave)
saldanha_bay <- map_dfr(dir("Data/wave_data/Saldanha Bay",
                        full.names = TRUE, pattern = "*.txt"), load_wave)

@@

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/temp_2014_2015/G1SST_fyears.RData")
load("~/Documents/Masters_2019/MastersProject/Data/temp_2014_2015/OISST_fyears.RData")
load("~/Documents/Masters_2019/MastersProject/Data/temp_2014_2015/MUR_fyears.RData")
load("~/Documents/Masters_2019/MastersProject/Data/temp_2014_2015/SACTN_fyears.RData")
load("~/Documents/Masters_2019/MastersProject/Data/temp_2014_2015/K10_fyears.RData")
```

Here i match the wave data with the datasets

@@

```

## Wavelet analyses on the wind data corresponding to the wavelet data showing temperature

```{r}

# When doing a wavelet analyses on the SACTN dataset the "insitu_temp" column needed to be renamed to "temp" for the rest of the code to run. The rest of this code is kept constant for each of the datasets (Remotely-sensed SST and In-situ seawater temperature)
# SACTN_fyears <- SACTN_fyears %>% 
#   dplyr::rename(temp = insitu_temp)

temp.d <- function(df){
temp.d <- df %>% 
  dplyr::group_by(site, date) %>% 
  dplyr::summarise(dirw_circ = mean(dirw_circ, na.rm = T)) %>%
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(site, no, dirw_circ, date)
}

temp.d <- temp.d(df = MUR_wind)
# temp.d <- temp.d(df = OISST_fyears)
# temp.d <- temp.d(df = G1SST_fyears) 
# temp.d <- temp.d(df = K10_fyears)

temp.d <- temp.d %>% 
  select(site, no, dirw_circ, date)

prewhite_fun <- function(x) {
  df <- x[, 2:3]
  out <- prewhiteAR(df, order = 3, method = "mle", aic = TRUE,
             genplot = FALSE, verbose = FALSE)
  colnames(out) <- c("no", "temp")
  return(out)
  }
PN_prewhite <- as.tibble(ddply(temp.d, .(site), prewhite_fun))

ggplot(PN_prewhite, aes(x = no, y = dirw)) +
  geom_hline(aes(yintercept = mean(dirw)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 4) +
  theme_bw()

wl.fun <- function(x) {
  analyze.wavelet(x, "temp", loess.span = 0, dt = 1,
                   dj = 1/50, lowerPeriod = 2, make.pval = TRUE, n.sim = 50, 
                   method = "white.noise", verbose = FALSE)
}

PN_wave <- dlply(PN_prewhite, .(site), wl.fun)

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures",plot_name,"_wind.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun)
```

>>>>

# Script Info
The aim of this script is to plot wind rose diagrams and wavelets representing the wind for the sites which correspond with the upwelling sites along the west coast of South Africa. Using this we will be able to make deductions as to whether or not the intensity and duration of upwelling varied as a result of wind patterns. *Latest wind data on line 149*

The wind data used in this analyses were obtained from the SAWS  *Other wind datasets still to be used*

@@

library(tidyverse)
library(ggpubr)
library(lubridate)
library(stringr)
library(circular)
library(broom)
library(purrr)
library(stlplus)
library(zoo)
source("functions/wind.rose.R")
```

@@

Creating a function to load the wind and wave data:

```{r define_fun8, include=TRUE}
# Building the  function (file path): data/wave_data/Sea Point/15m_359.txt
#                          1/   2     /    3    /     4

load_wave <- function(wave_files) {
  site_name <- sapply(strsplit(as.character(wave_files), "/"), "[[", 3)
  site_info <- sapply(strsplit(as.character(wave_files), "/"), "[[", 4)
  site_info <- sapply(strsplit(site_info, ".txt"), "[[", 1)
  site_info <- strsplit(site_info, "_")
  site_depth <- sapply(site_info, "[[", 1)
  site_num <- sapply(site_info, "[[", 2)

  wave <- read_table(wave_files, col_types = c("dddddd"),
                     col_names = c("date", "hs", "tp", "dir", "dirw", "spw")) %>%
    filter(tp != -999) %>%
    mutate(date = as.POSIXct(as.character(date), "%Y%m%d%H%M", tz = "Africa/Johannesburg")) %>%
    mutate(site = site_name,
           num = site_num,
           depth = site_depth) %>%
    select(site, num, depth, everything()) %>%
    na.omit()
  return(wave)
}

sea_point <- map_dfr(dir("Data/wave_data/Sea Point", 
                            full.names = TRUE, pattern = "*.txt"), load_wave)
lamberts_bay <- map_dfr(dir("Data/wave_data/Lamberts Bay", 
                          full.names = TRUE, pattern = "*.txt"), load_wave)
port_nolloth <- map_dfr(dir("Data/wave_data/Port Nolloth", 
                            full.names = TRUE, pattern = "*.txt"), load_wave)
saldanha_bay <- map_dfr(dir("Data/wave_data/Saldanha Bay",
                        full.names = TRUE, pattern = "*.txt"), load_wave)

@@

```{r}
load("Data/temp_2014_2015/G1SST_fyears.RData")
load("Data/temp_2014_2015/OISST_fyears.RData")
load("Data/temp_2014_2015/MUR_fyears.RData")
load("Data/temp_2014_2015/SACTN_fyears.RData")
load("Data/temp_2014_2015/K10_fyears.RData")
```

#############################################################
#############################################################
This following code is unable to plot the wind patterns (wind roses) as temperature collection occured between 2014-2015 and we do not have wind data that corresponds with these years

Here I match the wind data with the SST datasets

@@

```
#############################################################
#############################################################

## Writing a funciton to load the new wind data

Data/wind_data.txt(SAWS)/wind1/wind1.txt

```{r define_fun8, include=TRUE}
load_wind <- function(wind_files) {
 site_info <- sapply(strsplit(as.character(wind_files), "/"), "[[", 4)
 site_info <- sapply(strsplit(site_info, ".txt"), "[[", 1)

  wave <- read_table(wind_files, col_types = c("dddddd"),
                     col_names = c("station_number", "station_name", "date", "hour", "speed", "dir")) %>% 
       na.omit()
  return(wave)
}

tester <- map_dfr(dir("Data/wind_data.txt(SAWS)/wind1", 
                            full.names = TRUE, pattern = "*.txt"), load_wind)
```

### 2019-03-05 wavelets.Rmd
updated

Working with remotely-sensed SST and *in-situ* collected coastal seawater temperature, in the analyses bellow I aim to show how the intensity and duration of upwelling events varies per sites along the west coast of South Africa. It is important to remember that each of the datasets used within this study obtained SSTs at different resolutions. Here i was only required to plot a time series of 2 years.

@@

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
```

@@

* See the Dectect_MCS.Rmd script for more info. The datasets being loaded here are only for temperatures collected between the years 1992-2016. However if a longer time series is required changes may  be made to the Dectect_MCS.Rmd script (line 136)

@@

Here I only look at upwelling duration over a period of 1 year. from 2014 - 2015

@@

Creating a seasonal column. Allowing me to compare the intensity/duration of upwelling on a seasonal basis. This should to be repeated for each of the sites within each of the datasets (SACTN, MUR, OISST, G1SST and K10). The code bellow needs to be edited. Here I only focused on Port Nolloth within the SACTN dataset.

@@

```{r}
PN_14 <- SACTN_seasonal %>% 
  filter(site == "Port Nolloth") %>% 
  filter(year == 2014 )

PN_15 <- SACTN_seasonal %>% 
  filter(year == 2015 )
  # filter(site == "Port Nolloth") %>% 
  # filter(year == 2015 )

combined_seasonal <- function(df){
  plot <- df %>% 
    ggplot(aes(x = date, y = insitu_temp)) +
    geom_line() +
    facet_wrap(~season, ncol = 2, nrow = 2) +
    theme_bw()
}

combined_seasonal_2014 <- combined_seasonal(df = PN_14)
combined_seasonal_2015 <- combined_seasonal(df = PN_15)
combined_PortNolloth <- ggarrange(combined_seasonal_2014, combined_seasonal_2015)

# ggsave(plot = combined_PortNolloth, filename = "Figures/combined_PortNolloth.png")
```

Creating a wavelet analyses for the year 2015. This code creates a plot per season.

```{r}
seasonal_PN_15 <- PN_15 %>% 
  dplyr::rename(temp = insitu_temp)

@@

temp.d <- temp.d(df = seasonal_PN_15)

@@

PN_wave <- dlply(temp.d, .(site, season), wl.fun)

>>>>

## Script info

Wavelet anlyses showing the temperature variation between sites along the west coast for the years 2014 and 2015. Thereafter, wavelet analyses ae created per season for each individual site along the west coast of South Africa. Working with remotely-sensed SST and *in-situ* collected coastal seawater temperature, in the analyses bellow I aim to show how the intensity and duration of upwelling events vary between sites along the west coast of South Africa. It is important to remember that each of the datasets used within this study obtained SSTs at different resolutions.

@@

library(tidyverse)
library(ggpubr)
library(zoo)
library(lubridate)
library(stringr)
library(circular)
library(broom)
library(ggrepel)
library(purrr)
library(stlplus)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
# library(plyr)
```

@@

* See the Dectect_MCS.Rmd script for more info. The datasets loaded here are only for temperatures collected between the years 1992-2016. However if a longer time series is required changes may  be made to the Dectect_MCS.Rmd script (line 136)

@@

Examining the intensity and duration of upwelling for the years 2014 - 2015

@@

Creating a seasonal column. Allowing me to compare the intensity/duration of upwelling on a seasonal basis. This should to be repeated for each of the sites within each of the datasets (SACTN, MUR, OISST, G1SST and K10).

@@

```{r}
# PN_14 <- SACTN_seasonal %>% 
#   filter(site == "Port Nolloth") %>% 
#   filter(year == 2014 )

# creating a function to only select the year 2015
SST_season_func <- function(df){
seasonal_15 <- df %>% 
  filter(year == 2015 )
}

seasonal_2015_SACTN <- SST_season_func(df = SACTN_seasonal)
seasonal_2015_MUR <- SST_season_func(df = MUR_seasonal)
seasonal_2015_OISST <- SST_season_func(df = OISST_seasonal)
seasonal_2015_G1SST <- SST_season_func(df = G1SST_seasonal)
seasonal_2015_K10 <- SST_season_func(df = K10_seasonal)

## Plotting function
combined_seasonal <- function(df){
  plot <- df %>% 
    ggplot(aes(x = date, y = insitu_temp)) +
    geom_line() +
    facet_wrap(~season, ncol = 2, nrow = 2) +
    theme_bw()
}

combined_seasonal_2015_SACTN <- combined_seasonal(df = seasonal_2015_SACTN)
combined_seasonal_2015_MUR <- combined_seasonal(df = seasonal_2015_MUR)
combined_seasonal_2015_OISST <- combined_seasonal(df = seasonal_2015_OISST)
combined_seasonal_2015_G1SST <- combined_seasonal(df = seasonal_2015_G1SST)
combined_seasonal_2015K10 <- combined_seasonal(df = seasonal_2015_K10)
```

Creating a wavelet analyses for the year 2015. This code creates a plot per season. The outcome and plots of this code may be found in the figures folder->seasonal_wavelets (Figures/seasonal_wavelets)

# Here I rename the column "insitu-temp" to "temp", this is done in order to have it run on the same code as each of the other SST datasets
# seasonal_15 <- seasonal_2015_SACTN %>%
#   dplyr::rename(temp = insitu_temp)

@@

###### Remove the hash's to run the same code on each of these datasets####
# temp.d <- temp.d(df = seasonal_15)  for the SACTN  seawater temp dataset
# temp.d <- temp.d(df = seasonal_2015_MUR) #for the MUR SST dataset
# temp.d <- temp.d(df = seasonal_2015_OISST) #for the OISST SST dataset
# temp.d <- temp.d(df = seasonal_2015_G1SST) #for the G1SST SST dataset
# temp.d <- temp.d(df = seasonal_2015_K10) #for the K10 SST dataset

@@

sites_wave <- dlply(temp.d, .(site, season), wl.fun)

for (i in 1:length(sites_wave)) {
  attributes(sites_wave[[i]]) <- c(attributes(sites_wave[[i]]), ref = names(sites_wave)[i])
}
# x <- sites_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures/seasonal",plot_name,"_wavelets.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(sites_wave, plot_fun)
```

```{r}
temp.d <- temp.d %>% 
  select(season, site, no, temp)

temp_seasonal <- ggplot(temp.d, aes(x = date, y = temp)) +
  geom_line(aes(group = site)) +
  geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
  facet_wrap(~ season, nrow = 4) +
  theme_bw()

```
